Pillar 1 - Sequential Pattern Mining

### 2019-02-06 Pillar 1 - Sequential Pattern Mining.Rmd
debuged until CSPADE

```{r TODO}

@@

#
# Making sequences
sequences     <- make_sequence(item = item   )
sequences_PF  <- make_sequence(item = item_PF)
sequences_HL  <- make_sequence(item = item_HL)
#sequences_TNT <- make_sequence(data = d_transactions_not_taken, item = item_TNT) # compute ad hoc
#sequences_TPF <- make_sequence(data = d_transactions_not_taken, item = item_TPF) # compute ad hoc
sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )

@@

rm(make_sequence)
```

@@

rm(transactions)
```

@@

rm(transactions_TPF)
```

@@

#rm(d_support_grade, transactions_G)
```

@@

# Remove objects
rm(my_apriori, clean_AR, compute_metrics, make_AR,
   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G)
```

>>>>

@@

#
# Making sequences
sequences     <- make_sequence(item = item   )
sequences_PF  <- make_sequence(item = item_PF)
sequences_HL  <- make_sequence(item = item_HL)
#sequences_TPF <- make_sequence(data = d_transactions_TPF, item = item_TPF) # compute ad hoc
sequences_G   <- make_sequence(data = d_transactions_G    , item = item_G  )

@@

rm(make_sequence,
   d_transactions, d_transactions_TPF, d_transactions_G)
```

@@

rm(transactions, d_support_TNT)
```

@@

rm(transactions_TPF, d_support_PF_HL)
```

@@

rm(transactions_G, d_support_G)
```

@@

# Remove objects
rm(my_apriori, clean_AR, compute_metrics, editing_AR, make_AR,
   AR_taken, AR_PF, AR_HL, AR_TPF, AR_G,
   n_students)
```
